---
title: "Are men more judgmental than women?"
description: |
  This visualization explores whether or not there are gender differences in airplane judgments. There appears to be a small difference in childcare judgments, such that women consider it less rude to bring a baby or unruly child on a plane than men do. Gender differences of judgments seemingly differed across generations.
date: 03-8-2021
output:
  distill::distill_article:
    self_contained: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(rio)
library(here)
library(tidyverse)
data <- import(here("data", "flying-etiquette.csv"))

data <- data %>% filter(travel_frequency != "Never")


```

# Draft 1

```{r}

figure_4 <- data %>% 
  select(starts_with("rude"), gender) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "yes",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no") %>% 
  group_by(judgment, gender) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes,
         perc_no = no/total,
         perc_yes = yes/total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  select(-c(no, yes)) %>% 
  filter(judgment == "yes") %>% 
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor \nto walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor \nto go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats \nto be closer to friends",
                talk = "Talk to neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats \nto be closer to family")) %>% 
  filter(gender != "")

```


```{r,  echo = TRUE, layout = "l-body-outset"}
figure_4 %>% 
  ggplot(aes(x = perc, y = fct_reorder(type, perc), fill = gender)) +
  geom_bar(stat="identity") +
  theme_minimal()+
  colorblindr::scale_fill_OkabeIto(name = "Gender") +
  scale_x_continuous(limits = c(0, 1))+
  facet_wrap(~gender) +
  labs(x = "Percent judging the action as rude",
       y = NULL,
       title = "Are men more judgmental than women?")+
  theme(legend.position = "none",
        axis.text.x=element_blank())+
  geom_text(x = figure_4$perc, y = figure_4$type, 
            label = paste0(round(figure_4$perc*100), "%"),
            hjust = -.2)
  

```

In the first draft, I am plotting the percent who judge each action as rude and facet wrapping by gender. The numbers make it easy to compare female and male judgments. However, for my next draft, I want to be able to make the comparison more easily.

# Draft 2

```{r,echo = TRUE, layout = "l-body-outset"}
figure_4 %>% 
  ggplot(aes(x = perc, y = fct_reorder(type, perc), fill = gender)) +
  geom_bar(stat="identity", position=position_dodge()) +
  theme_minimal()+
  colorblindr::scale_fill_OkabeIto(name = "Gender") +
  scale_x_continuous(labels = scales::percent,
                     limits = c(0, 1))+
  labs(x = NULL,
       y = NULL,
       title = "Are men more judgmental than women?") +
  geom_vline(xintercept = 0.5, color = "gray40", linetype = "dashed")
```

In this draft, I used the `position_dodge()` argument to show the bars right next to each other. I also added a 50% vertical line so that you can see easily which actions are judged by rude by the majority of people. For the next draft, I am going to show this relation with a dumbbell plot/ connected dotplot. This will get rid of the unnecessary part of the bar that is not informative.

# Draft 3

```{r, echo = TRUE, layout = "l-body-outset"}

figure_4 %>% ggplot(aes(x = perc, y = fct_reorder(type, perc)))+
  geom_line(size = 3, color = "gray60") +
  geom_point(aes(color = gender), size = 4) +
  theme_minimal() +
  labs(x = "Percent judging the action as rude",
       y = NULL,
       title = "Are men more judgmental than women?")+
  theme(legend.direction = "horizontal",
        plot.title.position = "plot",
        legend.position = "bottom")+
  scale_x_continuous(labels = scales::percent,
                     limits = c(0,1))+
  colorblindr::scale_color_OkabeIto(name = "Gender") +
  geom_vline(xintercept = 0.5, color = "gray40", linetype = "dashed")


```

In my final draft, I wanted to color the bars so that it is really easy to see if one mean was greater than the other. Next, I wanted to facet wrap by age cohort because I noticed an interesting pattern in that women were less judgmental about bringing babies and children on planes. Since attitudes about gender roles are generational, I thought it would be interesting to see if this relationship occurred across different generations. I also created a theme and added a new font to the visualization.

# Final draft

```{r}
figure_4b <- data %>% 
  select(starts_with("rude"), gender, age) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "yes",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no") %>% 
  group_by(judgment, gender, age) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes,
         perc_no = no/total,
         perc_yes = yes/total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  select(-c(no, yes)) %>% 
  filter(judgment == "yes" & gender != "" & age != "") %>%
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor \nto walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor \nto go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats \nto be closer to friends",
                talk = "Talk to neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats \nto be closer to family"))


figure_4b$age <- factor(figure_4b$age, levels =
                         c("18-29",
                           "30-44",
                           "45-60",
                           "> 60"))
figure_4b <- figure_4b %>% 
  mutate(age = recode(age, "18-29" = "18 - 29 years old",
                      "30-44" = "30 - 44 years old",
                           "45-60" = "45 - 60 years old",
                           "> 60" = "Older than 60"))
```


```{r}
figure_4b <- figure_4b %>% select(-c(total, judgment)) %>% 
  pivot_wider(values_from = perc,
              names_from = gender) %>% 
  mutate(greater_gender = ifelse(Female > Male, "Female", "Male")) %>% 
  pivot_longer(cols = c("Female", "Male"),
               values_to = "perc",
               names_to = "gender")

```


```{r, echo = TRUE, layout = "l-body-outset", fig.height = 7, fig.width=5.5, preview=TRUE}
library(showtext)
font_add_google('Caveat Brush', "cb")
showtext_auto()

figure_4b %>% ggplot(aes(x = perc, y = fct_reorder(type, perc)))+
  geom_vline(xintercept = c(.25,.5, .75 ), color = "gray75")+
  geom_line(aes(color = greater_gender), size = 1.5) +
  scale_color_manual(values = c("#ffd780", "#8eccf0"), name = "Higher judgment") +
  ggnewscale::new_scale_color() + 
  geom_point(aes(color = gender), size = 3) +
  colorblindr::scale_color_OkabeIto(name = "Gender") +
  labs(x = "Percent judging the action as rude",
       y = NULL,
       title = "Are men more judgmental than women?",
       caption = "Data source: FiveThirtyEight")+
  theme_classic(base_size=15)+
  theme(legend.direction = "horizontal",
        plot.title.position = "plot",
        legend.position = "top",
        strip.text.x = element_text(face = "bold", size = 18, family = "cb"),
        strip.background = element_rect(colour = "black", fill = "#8eccf0", size = 1),
        panel.border = element_rect(linetype = "solid", size = 1, fill = NA),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(face = "bold", size = 40, family = "cb"),
        legend.key=element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_text(face = c("bold", "plain", "bold", "plain", 'bold', 'plain', 'bold', 'plain', 'bold')))+
  scale_x_continuous(labels = scales::percent,
                     limits = c(0,1),
                     expand = c(0,0),
                     breaks = c(.25, .5, .75))+
  facet_wrap(~age, ncol = 2)

```

