---
title: "Airplane etiquette"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    social: menu
    theme: flatly 
    source_code: https://github.com/sdimakis/dvfp
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(flexdashboard)
library(rio)
library(here)
library(tidyverse)
data <- import(here("data", "flying-etiquette.csv"))

```

Data Visualization 1 
=========================

 
Sidebar Title {.sidebar}
-----------------------------------------------------------------------

**Data source**

This data was collected online by [FiveThiryEight](https://fivethirtyeight.com/features/airplane-etiquette-recline-seat/) in late August, 2014. The researchers asked people whether or not they thought certain airplane behaviors were rude, such as reclining your seat or waking a neighbor to walk around. The researchers also inquired whether or not respondents had done these behaviors themselves. 

**Visualization 1**

This visualization plots the extent to which people consider airplane behaviors rude. The behaviors included are  moving to an unsold seat, talking to a neighbor, reclining your seat, asking someone to switch seats to sit by friends, asking someone to switch seats to sit by family, waking up a neighbor to go to the bathroom, waking up a neighbor to walk around, bringing a baby, and bringing an unruly child. Most people considered it rude to bring an unruly child and to wake up a neighbor to walk around, but other behaviors were considered not rude by the majority of the respondents. 

Row 
-----------------------------------------------------------------------

### Final
```{r, fig.width=14, fig.height=7}

figure_1 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "somewhat",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no" | judgment == "somewhat") %>% 
  group_by(judgment) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes + somewhat,
         perc_no = no/total,
         perc_yes = yes/total,
         perc_somewhat = somewhat/ total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  mutate(n = perc*total,
         perc = ifelse(judgment == "no", perc*-1, perc)) %>% 
  select(-c(no, yes, somewhat))

figure_1 <- figure_1 %>% 
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor \nto walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor \nto go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats \nto be closer to friends",
                talk = "Talk to your neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats \nto be closer to family"),
           judgment  = recode(judgment, no = "Not rude",
                             yes = "Very Rude",
                             somewhat = "Somewhat rude"))

figure_1_no <- figure_1 %>% filter(judgment == "Not rude")
figure_1_yes <- figure_1 %>% filter(judgment %in% c("Very Rude", "Somewhat rude"))

very_rude <- figure_1_yes %>% filter(judgment  == "Very Rude")
somewhat_rude <- figure_1_yes %>% filter(judgment  == "Somewhat rude")

ggplot() +
  geom_bar(data = figure_1_no, aes(x = perc, y = fct_reorder(type, perc), fill = judgment), 
           stat="identity",position="stack", width = .8, alpha = .8) +
  geom_bar(data = figure_1_yes, aes(x = perc, y = fct_reorder(type,perc), fill = forcats::fct_rev(judgment)), 
           stat = "identity", position = "stack", width = .8, alpha = .8) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")+
  geom_text(data = figure_1_no, aes(x=perc/2, y = type, label = paste0(abs(round(perc*100)),"%")),
            size = 4) +
  geom_text(data = very_rude, aes(x = ifelse(perc > .05, 
                                         somewhat_rude$perc + perc/2 , somewhat_rude$perc + perc),
                                  y = type, label = paste0(round(perc*100), "%")),
            size = 4, hjust = ifelse(very_rude$perc > .05, .4, -.2)) +
  geom_text(data = somewhat_rude, aes(x=perc/2, y = type, label = paste0(round(perc*100), "%")),
            size = 4) +
  colorblindr::scale_fill_OkabeIto(name = "")+
  scale_x_continuous(breaks = pretty(figure_1$perc), 
                     limits = c(-.9, .9),
                     labels = NULL)+
  theme_minimal(base_size = 20) +
  labs(x = NULL,
       y = NULL,
       title = "Airplane etiquette judgments",
       subtitle = "Is it rude to...") + 
  theme(legend.position = "bottom", 
         legend.direction = "horizontal",
        plot.title.position = "plot")


```

Row {data-width=350}
-----------------------------------------------------------------------


### V1
```{r}

figure_1 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), values_to = "judgment", names_prefix = "rude_", names_to = "type") %>%
  filter(judgment != "") %>% 
  group_by(judgment, type) %>% 
  count()

figure_1 %>% 
  ggplot(aes(x= type, y = n, fill = judgment)) +
  geom_bar(stat = "identity") + 
  coord_flip() +
  theme_minimal()
```

>This is my first attempt to plot responses to airplane etiquette questions. The first things that I wanted to fix were color (to a color palette better for people who are colorblind) and the scale from n to percents so that you can easily tell how many people thought each action was rude/ not rude. Last, I want to try making a "divergent" bar graph, which centers positive and negative judgments at zero.

### V2

```{r}

figure_1 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "yes",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no") %>% 
  group_by(judgment) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes,
         perc_no = no/total,
         perc_yes = yes/total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  mutate(n = perc*total,
         perc = ifelse(judgment == "no", perc*-1, perc)) %>% 
  select(-c(no, yes))

figure_1 <- figure_1 %>% 
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor to walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor to go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats to be closer to friends",
                talk = "Talk to neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats to be closer to family"),
           judgment  = recode(judgment, no = "Not rude",
                             yes = "Rude"))

figure_1 %>%
ggplot(aes(x = perc, y = fct_reorder(type, perc), fill = judgment)) +
  geom_bar(stat="identity",position="identity", width = .8) +
  colorblindr::scale_fill_OkabeIto(name = "Judgment")+
  scale_x_continuous(breaks = pretty(figure_1$perc), 
                     labels = paste0(abs(pretty(figure_1$perc))*100, "%"))+
  theme_minimal() +
  labs(x = NULL,
       y = NULL,
       title = "Airplane etiquette judgments")
```

>After some research, I found that a divergent bargraph is pretty difficult to do with more than two categories, so I started with this graph, collapsing down somewhat rude and very rude judgments in a category called "rude." Next, I wanted to change the etiquette type labels so that they are not so long and add in a third category for "somewhat" rude judgments.

### V2


```{r}

figure_1 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "somewhat",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no" | judgment == "somewhat") %>% 
  group_by(judgment) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes + somewhat,
         perc_no = no/total,
         perc_yes = yes/total,
         perc_somewhat = somewhat/ total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  mutate(n = perc*total,
         perc = ifelse(judgment == "no", perc*-1, perc)) %>% 
  select(-c(no, yes, somewhat))

figure_1 <- figure_1 %>% 
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor \nto walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor \nto go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats \nto be closer to friends",
                talk = "Talk to neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats \nto be closer to family"),
           judgment  = recode(judgment, no = "Not rude",
                             yes = "Very Rude",
                             somewhat = "Somewhat rude"))

figure_1_no <- figure_1 %>% filter(judgment == "Not rude")
figure_1_yes <- figure_1 %>% filter(judgment %in% c("Very Rude", "Somewhat rude"))

very_rude <- figure_1_yes %>% filter(judgment  == "Very Rude")
somewhat_rude <- figure_1_yes %>% filter(judgment  == "Somewhat rude")

ggplot() +
  geom_bar(data = figure_1_no, aes(x = perc, y = fct_reorder(type, perc), fill = judgment), 
           stat="identity",position="stack", width = .8, alpha = .8) +
  geom_bar(data = figure_1_yes, aes(x = perc, y = fct_reorder(type,perc), fill = forcats::fct_rev(judgment)), 
           stat = "identity", position = "stack", width = .8, alpha = .8) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed") +
  colorblindr::scale_fill_OkabeIto(name = "")+
  scale_x_continuous(breaks = pretty(figure_1$perc), 
                     limits = c(-.9, .9),
                     labels = paste0(abs(pretty(figure_1$perc*100)), "%"))+
  theme_minimal() +
  labs(x = NULL,
       y = NULL,
       title = "Airplane etiquette judgments",
       subtitle = "Is it rude to...") + 
  theme(legend.position = "bottom", 
         legend.direction = "horizontal",
        plot.title.position = "plot")

```

> In order to have three judgment categories (including somewhat rude), I had to use two different `geom_bar` lines, one for the negative values and one for the positive values. I also added a subtitle "Is it rude to..." so that the reader knows how the questions were asked. For my final, I will label the bars directly to reduce cognitive load.


Data Visualization 2
=========================

Sidebar Title {.sidebar}
-----------------------------------------------------------------------

**Data source**

This data was collected online by [FiveThiryEight](https://fivethirtyeight.com/features/airplane-etiquette-recline-seat/) in late August, 2014. The researchers asked people whether or not they thought certain airplane behaviors were rude, such as reclining your seat or waking a neighbor to walk around. The researchers also inquired whether or not respondents had done these behaviors themselves. 

**Visualization 2**

For the second visualization I wanted to highlight that behaviors that you could consider "essential" like waking up your neighbor because you need to go to the bathroom are rated as less rude than "non-essential" behaviors of the same consequence, like waking up your neighbor to walk around.

Row {data-width=650}
-----------------------------------------------------------------------

### Final

```{r, fig.width=14, fig.height=7}
figure_2 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "yes",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no") %>% 
  group_by(judgment) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes,
         perc_no = no/total,
         perc_yes = yes/total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  select(-c(no, yes)) %>% 
  filter(judgment == "yes") %>% 
  filter(type %in% c("baby", "child",
                     "switch_family", "switch_friends",
                     "wake_bathroom", "wake_walk")) %>% 
  mutate(essential = c("yes", "no", "yes", "no", "yes", "no"),
         type_cat = c("bring", "bring", "switch", "switch", "wake", "wake")) 


figure_2 <- figure_2 %>% 
  mutate(type_cat = recode(type_cat, bring = "Bring your \nchild",
                           wake = "Wake your\nneighbor",
                           switch = "Ask to \nswitch seats"),
         essential = recode(essential, no = "Non-essential",
                            yes = "Essential")) 

figure_2 %>% ggplot(aes(x = perc, y = fct_reorder(type_cat, perc)))+
  geom_line(size = 3, color = "#646667") +
  geom_point(aes(color = essential), size = 8) +
  theme_minimal(base_size = 20) +
  labs(x = "Percent of individuals that say it's rude to do action",
       y = NULL,
       title = "Essential and non-essential airplane etiquette judgments",
       subtitle = "Is it rude to...")+
  theme(legend.direction = "horizontal",
        plot.title.position = "plot",
        legend.position = "bottom")+
  scale_x_continuous(labels = scales::percent,
                     limits = c(0,1))+
  colorblindr::scale_color_OkabeIto(name = "Reason")


  
```

Row {data-width=350}
-----------------------------------------------------------------------

### V1

```{r}

figure_2 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "yes",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no") %>% 
  group_by(judgment) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes,
         perc_no = no/total,
         perc_yes = yes/total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  select(-c(no, yes)) %>% 
  filter(judgment == "yes") %>% 
  filter(type %in% c("baby", "child",
                     "switch_family", "switch_friends",
                     "wake_bathroom", "wake_walk"))

figure_2 <- figure_2 %>% 
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor \nto walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor \nto go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats \nto be closer to friends",
                talk = "Talk to neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats \nto be closer to family"),
         essential = c("yes", "no", "yes", "no", "yes", "no"),
         type_cat = c("bring", "bring", "switch", "switch", "wake", "wake"))


figure_2 %>% ggplot(aes(x = type_cat, y = perc, fill = essential)) +
  geom_bar(stat="identity", position=position_dodge()) +
  coord_flip() +
  theme_minimal()
```

> Here I am plotting airplane etiquette judgments, colored by how essential the action is. For example, waking someone up to walk around is less essential than waking up someone to go to the bathroom, so it should be judged as more rude. Instead of breaking it up by category like I'm doing here, I'm going to plot them all in order and show each category with a different color.

### V2

```{r}


figure_2 %>% 
  ggplot(aes(x = perc, y = fct_reorder(type, perc))) +
  geom_col(aes(fill = type_cat), alpha = .8) +
  labs(x = "Percent of individuals that say it's rude to do action",
       y = NULL,
       title = "Airplane etiquette judgments for essential and nonessential behaviors",
       subtitle = "How rude is to...")+
  theme_minimal()+
  scale_x_continuous(labels = scales::percent)+
  colorblindr::scale_fill_OkabeIto()+ 
  theme(legend.position = "none",
        plot.title.position = "plot")
```

> I like this plot a lot, but I want to put it in context of all the judgments (not just these six). I will first plot all of the judgments, then use color to highlight the ones shown here.  

### V3

```{r}
figure_2 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "yes",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no") %>% 
  group_by(judgment) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes,
         perc_no = no/total,
         perc_yes = yes/total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  select(-c(no, yes)) %>% 
  filter(judgment == "yes")

figure_2 <- figure_2 %>% 
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor \nto walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor \nto go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats \nto be closer to friends",
                talk = "Talk to your neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats \nto be closer to family"),
         type_cat = c("bring", "bring", NA, "switch", "switch", NA, NA, "wake", "wake"))

figure_2 %>% 
  ggplot(aes(x = perc, y = fct_reorder(type, perc))) +
  geom_col(fill = "gray60", alpha = .8)+
  geom_col(aes(fill = type_cat), alpha = .8) +
  labs(x = "Percent of individuals that say it's rude to do action",
       y = NULL,
       title = "Airplane etiquette judgments for essential and nonessential behaviors",
       subtitle = "How rude is to...")+
  theme_minimal()+
  scale_x_continuous(labels = scales::percent,
                     limits = c(0,.85))+
  colorblindr::scale_fill_OkabeIto()+ 
  theme(legend.position = "none",
        plot.title.position = "plot")+
  geom_text(x = figure_2$perc, y = figure_2$type, 
            label = paste0(round(figure_2$perc*100), "%"),
            hjust = -.2)

```

> I think this is good as it's going to get for a bar plot. For my final plot, I want it to be clear that I'm directly comparing essential to nonessential behaviors. To do this, I want them to be plotted on the same line. I'm going to use a dumbbell/ lollipop plot to do this.

Data Visualization 3
=========================

Sidebar Title {.sidebar}
-----------------------------------------------------------------------

**Data source**

This data was collected online by [FiveThiryEight](https://fivethirtyeight.com/features/airplane-etiquette-recline-seat/) in late August, 2014. The researchers asked people whether or not they thought certain airplane behaviors were rude, such as reclining your seat or waking a neighbor to walk around. The researchers also inquired whether or not respondents had done these behaviors themselves. 

**Visualization 3**

I created this final visualization to demonstrate if judgments change when the action is personal. This visualization shows the distribution of respondent height for each answer to the question "is it rude to recline your seat on an airplane?" Since people who are tall may be made more uncomfortable by someone reclining their seat, they may feel more strongly that it is rude. There looks to be a small (and likely insignificant) effect, where respondents who said that the behavior was very rude were slightly taller than those who said it was somewhat rude or not rude at all. 

Row
-----------------------------------------------------------------------

### Final

```{r, fig.width=14, fig.height=7}

height_inches = NULL
height <- function(x){
for(i in 1:length(x)){
  temp <- str_split_fixed(x[i], "\"\"", n = 2)
  temp2 <- str_split_fixed(temp[1], "'", n = 2)
  temp3 <- as.numeric(temp2[1])*12 + as.numeric(temp2[2])
  height_inches <- append(height_inches, temp3)
  i <- i +1
}
  return(height_inches)
}

figure_3 <- data %>% mutate(height_inches = height(data$height))
figure_3 <- figure_3 %>% select(height_inches, n_get_up, rude_recline, children, rude_baby, rude_child) %>% 
  filter(rude_recline != "")



figure_3 <- figure_3 %>% mutate(rude_recline = recode(rude_recline,
                                          `Yes, very rude` = "Very rude",
                                          `Yes, somewhat rude` = "Somewhat \nrude",
                                          `No, not rude at all` = "Not rude"))


means <- figure_3 %>% 
  group_by(rude_recline) %>% 
  summarize(mean = mean(height_inches, na.rm = TRUE))

figure_3 %>% 
  ggplot(aes(x = rude_recline, y = height_inches)) +
  theme_minimal(base_size = 20)+
  coord_flip()+
  ggforce::geom_sina(aes(color = rude_recline))+
  labs(y = "Height of judger (in inches)",
       x = NULL,
       title = "How reclining behavior is judged by height",
       subtitle = expression(paste("Is it rude to ", italic("recline"), 
                                   " your seat on an airplane?")))+
  geom_segment(aes(x = .8, xend= 1.2, y=means[[1,2]], yend=means[[1,2]]), size =1 ) +
  geom_segment(aes(x = 1.8, xend= 2.2, y=means[[2,2]], yend=means[[2,2]]), size = 1) +
  geom_segment(aes(x = 2.8, xend= 3.2, y=means[[3,2]], yend=means[[3,2]]), size = 1) +
  geom_point(data = means, aes(y = mean, x = rude_recline), size = 4) +
  geom_label(label = round(means[[1,2]], 2), x = 1.4, y = means[[1,2]], size = 7) +
  geom_label(label = round(means[[2,2]], 2), x = 2.4, y = means[[2,2]], size = 7) +
  geom_label(label = round(means[[3,2]], 2), x = 3.4, y = means[[3,2]], size = 7) +
  theme(legend.position = "none",
        plot.title.position = "plot")+
  colorblindr::scale_color_OkabeIto()

```

Row 
-----------------------------------------------------------------------

### V1

```{r}

height_inches = NULL
height <- function(x){
for(i in 1:length(x)){
  temp <- str_split_fixed(x[i], "\"\"", n = 2)
  temp2 <- str_split_fixed(temp[1], "'", n = 2)
  temp3 <- as.numeric(temp2[1])*12 + as.numeric(temp2[2])
  height_inches <- append(height_inches, temp3)
  i <- i +1
}
  return(height_inches)
}

figure_3 <- data %>% mutate(height_inches = height(data$height))
figure_3 <- figure_3 %>% select(height_inches, n_get_up, rude_recline, children, rude_baby, rude_child) %>% 
  filter(rude_recline != "")

figure_3 %>% 
  ggplot(aes(x = rude_recline, y = height_inches)) +
  geom_boxplot()+
  theme_minimal()+
  coord_flip()

```

> In this first draft, I am plotting boxplots of judger height by judgment (very rude, somewhat rude, or not rude). This is a very basic boxplot and I will add color to distingh the boxes from each other, points so that you can see the data, and labels in the next plot. 

### V2

```{r}

figure_3 %>% 
  ggplot(aes(x = rude_recline, y = height_inches)) +
  geom_boxplot(aes(fill = rude_recline))+
  theme_minimal()+
  coord_flip()+
  geom_jitter()+
  labs(y = "Height of judger (in inches)",
       x = NULL,
       title = "How reclining behavior is judged by height",
       subtitle = "Is it rude to recline your seat on an airplane?")+
  theme(legend.position = "none",
        plot.title.position = "plot")+
  colorblindr::scale_fill_OkabeIto()
```

> In this draft, I am using `geom_jitter()` so that you can see the points that would otherwise be stacked on top of each other. I think the points are distracting here because there are two many points to easily be able to tell distribution patterns. In the next draft I will use a sina plot to plot the distribution of points.

### V3

```{r}

figure_3 <- figure_3 %>% mutate(rude_recline = recode(rude_recline,
                                          `Yes, very rude` = "Very rude",
                                          `Yes, somewhat rude` = "Somewhat \nrude",
                                          `No, not rude at all` = "Not rude"))

figure_3 %>% 
  ggplot(aes(x = rude_recline, y = height_inches)) +
  theme_minimal()+
  coord_flip()+
  ggforce::geom_sina(aes(color = rude_recline))+
  labs(y = "Height of judger (in inches)",
       x = NULL,
       title = "How reclining behavior is judged by height",
       subtitle = expression(paste("Is it rude to ", italic("recline"), 
                                   " your seat on an airplane?")))+
  theme(legend.position = "none",
        plot.title.position = "plot")+
  colorblindr::scale_color_OkabeIto()


```

> In this draft, I am using a sina plot from the `geom_force()` package in order to see the distribution of the points. I got rid of the boxplot because I felt like it distracting. I do want to be able to easily decern the mean easily from the graph, so I will add a point for each mean and a label to my final draft.