---
title: "Data visualization 1"
description: |
  This visualization plots the extent to which people consider airplane behaviors rude. The behaviors included are  moving to an unsold seat, talking to a neighbor, reclining your seat, asking someone to switch seats to sit by friends, asking someone to switch seats to sit by family, waking up a neighbor to go to the bathroom, waking up a neighbor to walk around, bringing a baby, and bringing an unruly child. Most people considered it rude to bring an unruly child and to wake up a neighbor to walk around, but other behaviors were considered not rude by the majority of the respondents. 

author:
  - name: Sarah Dimakis
    url: https://github.com/sdimakis
    affiliation: University of Oregon
date: 03-08-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(flexdashboard)
library(rio)
library(here)
library(tidyverse)
data <- import(here("data", "flying-etiquette.csv"))

data <- data %>% filter(travel_frequency != "Never")

```



```{r, fig.width=14, fig.height=7}

figure_1 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "somewhat",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no" | judgment == "somewhat") %>% 
  group_by(judgment) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes + somewhat,
         perc_no = no/total,
         perc_yes = yes/total,
         perc_somewhat = somewhat/ total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  mutate(n = perc*total,
         perc = ifelse(judgment == "no", perc*-1, perc)) %>% 
  select(-c(no, yes, somewhat))

figure_1 <- figure_1 %>% 
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor \nto walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor \nto go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats \nto be closer to friends",
                talk = "Talk to your neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats \nto be closer to family"),
           judgment  = recode(judgment, no = "Not rude",
                             yes = "Very Rude",
                             somewhat = "Somewhat rude"))

figure_1_no <- figure_1 %>% filter(judgment == "Not rude")
figure_1_yes <- figure_1 %>% filter(judgment %in% c("Very Rude", "Somewhat rude"))

very_rude <- figure_1_yes %>% filter(judgment  == "Very Rude")
somewhat_rude <- figure_1_yes %>% filter(judgment  == "Somewhat rude")

ggplot() +
  geom_bar(data = figure_1_no, aes(x = perc, y = fct_reorder(type, perc), fill = judgment), 
           stat="identity",position="stack", width = .8, alpha = .8) +
  geom_bar(data = figure_1_yes, aes(x = perc, y = fct_reorder(type,perc), fill = forcats::fct_rev(judgment)), 
           stat = "identity", position = "stack", width = .8, alpha = .8) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed")+
  geom_text(data = figure_1_no, aes(x=perc/2, y = type, label = paste0(abs(round(perc*100)),"%")),
            size = 4) +
  geom_text(data = very_rude, aes(x = ifelse(perc > .05, 
                                         somewhat_rude$perc + perc/2 , somewhat_rude$perc + perc),
                                  y = type, label = paste0(round(perc*100), "%")),
            size = 4, hjust = ifelse(very_rude$perc > .05, .4, -.2)) +
  geom_text(data = somewhat_rude, aes(x=perc/2, y = type, label = paste0(round(perc*100), "%")),
            size = 4) +
  colorblindr::scale_fill_OkabeIto(name = "")+
  scale_x_continuous(breaks = pretty(figure_1$perc), 
                     limits = c(-.9, .9),
                     labels = NULL)+
  theme_minimal(base_size = 20) +
  labs(x = NULL,
       y = NULL,
       title = "Airplane etiquette judgments",
       subtitle = "Is it rude to...") + 
  theme(legend.position = "bottom", 
         legend.direction = "horizontal",
        plot.title.position = "plot")


```



### Draft 1
```{r}

figure_1 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), values_to = "judgment", names_prefix = "rude_", names_to = "type") %>%
  filter(judgment != "") %>% 
  group_by(judgment, type) %>% 
  count()

figure_1 %>% 
  ggplot(aes(x= type, y = n, fill = judgment)) +
  geom_bar(stat = "identity") + 
  coord_flip() +
  theme_minimal()
```

>This is my first attempt to plot responses to airplane etiquette questions. The first things that I wanted to fix were color (to a color palette better for people who are colorblind) and the scale from n to percents so that you can easily tell how many people thought each action was rude/ not rude. Last, I want to try making a "divergent" bar graph, which centers positive and negative judgments at zero.

### Draft 2

```{r}

figure_1 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "yes",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no") %>% 
  group_by(judgment) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes,
         perc_no = no/total,
         perc_yes = yes/total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  mutate(n = perc*total,
         perc = ifelse(judgment == "no", perc*-1, perc)) %>% 
  select(-c(no, yes))

figure_1 <- figure_1 %>% 
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor to walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor to go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats to be closer to friends",
                talk = "Talk to neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats to be closer to family"),
           judgment  = recode(judgment, no = "Not rude",
                             yes = "Rude"))

figure_1 %>%
ggplot(aes(x = perc, y = fct_reorder(type, perc), fill = judgment)) +
  geom_bar(stat="identity",position="identity", width = .8) +
  colorblindr::scale_fill_OkabeIto(name = "Judgment")+
  scale_x_continuous(breaks = pretty(figure_1$perc), 
                     labels = paste0(abs(pretty(figure_1$perc))*100, "%"))+
  theme_minimal() +
  labs(x = NULL,
       y = NULL,
       title = "Airplane etiquette judgments")
```

>After some research, I found that a divergent bargraph is pretty difficult to do with more than two categories, so I started with this graph, collapsing down somewhat rude and very rude judgments in a category called "rude." Next, I wanted to change the etiquette type labels so that they are not so long and add in a third category for "somewhat" rude judgments.

### Draft 3


```{r}

figure_1 <- data %>% 
  select(starts_with("rude")) %>% 
  pivot_longer(cols = starts_with("rude"), 
               values_to = "judgment", 
               names_prefix = "rude_", 
               names_to = "type") %>%
  mutate(judgment = recode(judgment, "No, not rude at all" = "no",
         "Yes, somewhat rude" = "somewhat",
         "Yes, very rude" = "yes")) %>% 
  filter(judgment == "yes" | judgment == "no" | judgment == "somewhat") %>% 
  group_by(judgment) %>% 
  count(type) %>% 
  pivot_wider(names_from = judgment,
              values_from = n) %>% 
  mutate(total = no + yes + somewhat,
         perc_no = no/total,
         perc_yes = yes/total,
         perc_somewhat = somewhat/ total) %>% 
  pivot_longer(cols = starts_with("perc"),
               values_to = "perc",
               names_prefix = "perc_",
               names_to = "judgment") %>% 
  mutate(n = perc*total,
         perc = ifelse(judgment == "no", perc*-1, perc)) %>% 
  select(-c(no, yes, somewhat))

figure_1 <- figure_1 %>% 
  mutate(type = recode(type, child = "Bring an unruly child",
                wake_walk = "Wake neighbor \nto walk around",
                recline = "Recline your seat",
                wake_bathroom = "Wake neighbor \nto go to the bathroom",
                baby = "Bring a baby",
                switch_friends = "Ask to switch seats \nto be closer to friends",
                talk = "Talk to neighbor",
                unsold = "Move to an unsold seat",
                switch_family = "Ask to switch seats \nto be closer to family"),
           judgment  = recode(judgment, no = "Not rude",
                             yes = "Very Rude",
                             somewhat = "Somewhat rude"))

figure_1_no <- figure_1 %>% filter(judgment == "Not rude")
figure_1_yes <- figure_1 %>% filter(judgment %in% c("Very Rude", "Somewhat rude"))

very_rude <- figure_1_yes %>% filter(judgment  == "Very Rude")
somewhat_rude <- figure_1_yes %>% filter(judgment  == "Somewhat rude")

ggplot() +
  geom_bar(data = figure_1_no, aes(x = perc, y = fct_reorder(type, perc), fill = judgment), 
           stat="identity",position="stack", width = .8, alpha = .8) +
  geom_bar(data = figure_1_yes, aes(x = perc, y = fct_reorder(type,perc), fill = forcats::fct_rev(judgment)), 
           stat = "identity", position = "stack", width = .8, alpha = .8) +
  geom_vline(xintercept = 0, color = "black", linetype = "dashed") +
  colorblindr::scale_fill_OkabeIto(name = "")+
  scale_x_continuous(breaks = pretty(figure_1$perc), 
                     limits = c(-.9, .9),
                     labels = paste0(abs(pretty(figure_1$perc*100)), "%"))+
  theme_minimal() +
  labs(x = NULL,
       y = NULL,
       title = "Airplane etiquette judgments",
       subtitle = "Is it rude to...") + 
  theme(legend.position = "bottom", 
         legend.direction = "horizontal",
        plot.title.position = "plot")

```

> In order to have three judgment categories (including somewhat rude), I had to use two different `geom_bar` lines, one for the negative values and one for the positive values. I also added a subtitle "Is it rude to..." so that the reader knows how the questions were asked. For my final, I will label the bars directly to reduce cognitive load.