---
title: "datavis_3"
description: |
  I created this final visualization to demonstrate if judgments change when the action is personal. This visualization shows the distribution of respondent height for each answer to the question "is it rude to recline your seat on an airplane?" Since people who are tall may be made more uncomfortable by someone reclining their seat, they may feel more strongly that it is rude. There looks to be a small (and likely insignificant) effect, where respondents who said that the behavior was very rude were slightly taller than those who said it was somewhat rude or not rude at all. 
author:
  - name: Sarah Dimakis
    url: https://github.com/sdimakis
date: 03-08-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(flexdashboard)
library(rio)
library(here)
library(tidyverse)
data <- import(here("data", "flying-etiquette.csv"))

data <- data %>% filter(travel_frequency != "Never")

```



**Visualization 3**

### Final

```{r, fig.width=14, fig.height=7}

height_inches = NULL
height <- function(x){
for(i in 1:length(x)){
  temp <- str_split_fixed(x[i], "\"\"", n = 2)
  temp2 <- str_split_fixed(temp[1], "'", n = 2)
  temp3 <- as.numeric(temp2[1])*12 + as.numeric(temp2[2])
  height_inches <- append(height_inches, temp3)
  i <- i +1
}
  return(height_inches)
}

figure_3 <- data %>% mutate(height_inches = height(data$height))
figure_3 <- figure_3 %>% select(height_inches, n_get_up, rude_recline, children, rude_baby, rude_child) %>% 
  filter(rude_recline != "")



figure_3 <- figure_3 %>% mutate(rude_recline = recode(rude_recline,
                                          `Yes, very rude` = "Very rude",
                                          `Yes, somewhat rude` = "Somewhat \nrude",
                                          `No, not rude at all` = "Not rude"))


means <- figure_3 %>% 
  group_by(rude_recline) %>% 
  summarize(mean = mean(height_inches, na.rm = TRUE))

figure_3 %>% 
  ggplot(aes(x = rude_recline, y = height_inches)) +
  theme_minimal(base_size = 20)+
  coord_flip()+
  ggforce::geom_sina(aes(color = rude_recline))+
  labs(y = "Height of judger (in inches)",
       x = NULL,
       title = "How reclining behavior is judged by height",
       subtitle = expression(paste("Is it rude to ", italic("recline"), 
                                   " your seat on an airplane?")))+
  geom_segment(aes(x = .8, xend= 1.2, y=means[[1,2]], yend=means[[1,2]]), size =1 ) +
  geom_segment(aes(x = 1.8, xend= 2.2, y=means[[2,2]], yend=means[[2,2]]), size = 1) +
  geom_segment(aes(x = 2.8, xend= 3.2, y=means[[3,2]], yend=means[[3,2]]), size = 1) +
  geom_point(data = means, aes(y = mean, x = rude_recline), size = 4) +
  geom_label(label = round(means[[1,2]], 2), x = 1.4, y = means[[1,2]], size = 7) +
  geom_label(label = round(means[[2,2]], 2), x = 2.4, y = means[[2,2]], size = 7) +
  geom_label(label = round(means[[3,2]], 2), x = 3.4, y = means[[3,2]], size = 7) +
  theme(legend.position = "none",
        plot.title.position = "plot")+
  colorblindr::scale_color_OkabeIto()

```

### Draft 1

```{r}

figure_3 <- data %>% mutate(height_inches = height(data$height))
figure_3 <- figure_3 %>% select(height_inches, n_get_up, rude_recline, children, rude_baby, rude_child) %>% 
  filter(rude_recline != "")

figure_3 %>% 
  ggplot(aes(x = rude_recline, y = height_inches)) +
  geom_boxplot()+
  theme_minimal()+
  coord_flip()

```

> In this first draft, I am plotting boxplots of judger height by judgment (very rude, somewhat rude, or not rude). This is a very basic boxplot and I will add color to distingh the boxes from each other, points so that you can see the data, and labels in the next plot. 

### Draft 2

```{r}

figure_3 %>% 
  ggplot(aes(x = rude_recline, y = height_inches)) +
  geom_boxplot(aes(fill = rude_recline))+
  theme_minimal()+
  coord_flip()+
  geom_jitter()+
  labs(y = "Height of judger (in inches)",
       x = NULL,
       title = "How reclining behavior is judged by height",
       subtitle = "Is it rude to recline your seat on an airplane?")+
  theme(legend.position = "none",
        plot.title.position = "plot")+
  colorblindr::scale_fill_OkabeIto()
```

> In this draft, I am using `geom_jitter()` so that you can see the points that would otherwise be stacked on top of each other. I think the points are distracting here because there are two many points to easily be able to tell distribution patterns. In the next draft I will use a sina plot to plot the distribution of points.

### Draft 3

```{r}

figure_3 <- figure_3 %>% mutate(rude_recline = recode(rude_recline,
                                          `Yes, very rude` = "Very rude",
                                          `Yes, somewhat rude` = "Somewhat \nrude",
                                          `No, not rude at all` = "Not rude"))

figure_3 %>% 
  ggplot(aes(x = rude_recline, y = height_inches)) +
  theme_minimal()+
  coord_flip()+
  ggforce::geom_sina(aes(color = rude_recline))+
  labs(y = "Height of judger (in inches)",
       x = NULL,
       title = "How reclining behavior is judged by height",
       subtitle = expression(paste("Is it rude to ", italic("recline"), 
                                   " your seat on an airplane?")))+
  theme(legend.position = "none",
        plot.title.position = "plot")+
  colorblindr::scale_color_OkabeIto()


```

> In this draft, I am using a sina plot from the `geom_force()` package in order to see the distribution of the points. I got rid of the boxplot because I felt like it distracting. I do want to be able to easily decern the mean easily from the graph, so I will add a point for each mean and a label to my final draft.